SDR enhancement by clouds

### 2024-03-13 article/article.Rmd
Commit 2024-03-13 20:15

@@

@@

- measured data
- available data
  - sky cam
  - chp1
  - cm21
  - cimel
- CSid tool

The recording of the signal is the one minute average.
Thus we will refer to this time scale as a cloud enhancement event (CE).
Due to the instruments response time.....

## Data quality control

..  todo ...

## Data selection

>>>>

<!-- Define CE and ECE -->
In this study, we define as cloud enhancement events (CE) the cases when the measured
global horizontal irradiance (GHI) at ground level exceeds the expected value under
sky, unobscured by clouds.
Similar, we define the extreme cloud enhancement events (ECE), the cases when GHI,
exceeds the Total Solar Irradiance on horizontal plane at ground level.

@@

## GHI data

@@

In this study, we evaluate the effects

- available data
  - sky cam
  - chp1
  - cm21
  - cimel
- CSid tool

The recording of the signal is the one minute average.
Thus we will refer to this time scale as a cloud enhancement event (CE).
